Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex
Modify some sections, comment the figure inclusion to allow compilation

@@

\subsubsection(Aimbots)
Aimbots are a sub set of game hacks. These reffer to scripts that run on the client side of the game 
and track things such as hit boxes of other players in the game and aim for you once activated. It is 
an easy kind of cheat to spot as it will usually result in unhuman reflexes or movement or such things 
as wall tracking where a player is aiming at you through a wall. Since they also track only specific 
areas, a statistical analysis of the areas where the player regularly hit his targets can reveal whether 
or not he was hacking. Normal humans can't aim at the same target over a long period of time and will
usually stay within one or two standard deviations of the mean for any given area. Someone who aimbots 
on the other hand will usually have one area that is way above the mean.

\subsubsection (Wall Hacks)
There are several versions of this cheat but there is usually two types: a script that uses a bug from the
developer to allow the user to view more than he should be making walls transparent or "see-through"; another would be to make walls non solid objects allowing the player to shoot through walls or even hide in them. These hacks usually relly on the fact the FPS games in particular send only the raw positional information of players and let the player or client's 3D renderer to hide other players behind walls or through "fog of war". These can be turned off from the client side and thus make it look like the players are moving around what seams like an empty space. Obviously a completely empty map serves no purpose for the hacker as he couldn't navigate the map properly either. This third party software allows the user to only hide certain surfaces from its client 3D renderer so that the hacker may have an edge compared to other players.

\subsubsection(Nuking or artificial lag)
The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage. In some games, hits aren't registered until the server registeres a hit.

@@

@@

\subsubsection{Jombah}
Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and ___ comments. He still passes the threshold for being a key player but the reason he is being focused on is due to his product. Jombah sells Fortnite accounts which is one of the crimewares we are focusing on. Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify. Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers. Jombah’s relevance lies not with his stellar service but with the product he provides.

>>>>

\usepackage{graphicx}

@@

\subsubsection{Aimbots}
Aimbots are a sub set of game hacks. These reffer to scripts that run on the client side of the game 
and track things such as hit boxes of other players in the game and aim for you once activated. It is 
an easy kind of cheat to spot as it will usually result in unhuman reflexes or movement or such things 
as wall tracking where a player is aiming at you through a wall. Since they also track only specific 
areas, a statistical analysis of the areas where the player regularly hit his targets can reveal whether 
or not he was hacking. Normal humans can't aim at the same target over a long period of time and will
usually stay within one or two standard deviations of the mean for any given area. Someone who aimbots 
on the other hand will usually have one area that is way above the mean.

\subsubsection{Hacks}
There are several versions of this cheat but there is usually two types: a script that uses a bug from the
developer to allow the user to view more than he should be making walls transparent or "see-through"; another would be to make walls non solid objects allowing the player to shoot through walls or even hide in them. These hacks usually relly on the fact the FPS games in particular send only the raw positional information of players and let the player or client's 3D renderer to hide other players behind walls or through "fog of war". These can be turned off from the client side and thus make it look like the players are moving around what seams like an empty space. Obviously a completely empty map serves no purpose for the hacker as he couldn't navigate the map properly either. This third party software allows the user to only hide certain surfaces from its client 3D renderer so that the hacker may have an edge compared to other players.

\subsubsection{Nuking or artificial lag}
The sub genre of hacks, as its name suggests, consists of artificially generating lag between the client and the server in order to gain an advantage. In some games, hits aren't registered until the server registeres a hit.

@@

% this is not compiling

% \begin{figure}
% \centering
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width = .4\linewidth]{ThreadCount}
% 	\caption{Thread Count}
% 	\label{fig:thread count}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% 	\centering
% 	\includegraphics[width=.4\linewidth]{Comment Count}
% 	\caption{Comment Count}
% 	\label{fig:comment count}
% \end{subfigure}
% \caption{Thread and Comment Pie Charts}
% \label{fig:thread and comment charts}
% \end{figure}

@@

\subsubsection{Jombah}
Jombah is also considered a key player on the Fortnite hacker forums even though he is on the lower end of the thread and comment counts with only two threads and [NUMBER] comments. He still passes the threshold for being a key player but the reason he is being focused on is due to his product. Jombah sells Fortnite accounts which is one of the crimewares we are focusing on. Jombah’s products are “premium” accounts which he appears to sell for a relatively cheap price as compared to other sellers though unlike some other sellers he does not offer custom accounts that a buyer can specify. Jombah is also a decently active user on hackerforum.net though not as active as Wyattz or as well liked by his customers. Jombah’s relevance lies not with his stellar service but with the product he provides.
